---
title: "tryout_abm"
author: "SKK"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse)

```

# get probabilities
```{r venner}
procent <- c(1,
    2,
    5,
    8,
    12,
    20,
    10,
    4,
    6,
    2,
    30)

ven_prob <- procent/100
# sum(procent) #test hvis det giver 100%
#n_numb <- 1430 #antal respondenter
```

```{r introvert/extrovert}
#from Emma and Mias work
ie_prob <-   c(0.05, 0.15, 0.15, 0.1, 0.1, 0.15, 0.15, 0.1, 0.05)

#or just a batteri som 0-10 with mean 5 and sd 2, meaning that having a battery of 1 or 9 is extreme cases and that most people lie with in 1-9 = 95%
library(truncnorm)
hist(rtruncnorm(n=1000, a=1, b=10, mean=5, sd=2))
hist <- hist(rtruncnorm(n=1000, a=1, b=10, mean=5, sd=2))
soba_prob <- hist$density #probability for each increment from 0-10 on batteri scale
```

```{r fritidsinteresser}
setwd("C:/Users/sarak/OneDrive - Aarhus universitet/26102021/Cog sci/4_semester/EXAMS/SoCult/data")
fritid <- read.csv("fritidsinteresser2022.csv",header=TRUE,sep=";")
# 14 forskellige kategorier, der er værd at tage med (to steder er (angivet med +) er underkategorien taget fra, som at simplificere)

fritid <- fritid %>% 
  rowwise() %>% 
  mutate(mean = mean(c(X1:X4))) #create mean over kvartaler

int_prob <- fritid$mean/100 #probability per fritidsinteresse i samme rækkefølge som i dataframet
```

```{r saved probabilties written out}
ie_prob <- c(0.05, 0.15, 0.15, 0.10, 0.10, 0.15, 0.15, 0.10, 0.05) #Introvert/extrovert prob on scale from 1 - 10. From Emma and Mie
int_prob <- c(0.955, 0.955, 0.435, 0.645, 0.625, 0.545, 0.390, 0.325, 0.845, 0.750, 0.320, 0.355, 0.250, 0.215) #Interest probabilities. 14 different interests taken from Statistikbanken.
ven_prob <- c(0.01, 0.02, 0.05, 0.08, 0.12, 0.20, 0.10, 0.04, 0.06, 0.02, 0.30) #Probabilities of having different number of friends. Taken from Vive paper
```

# Prepare ABM environment
## global variables
```{r global}
#saved stuff
setwd('.')
load("prob+tables.RData") #not updated

iterations <- 120    #How many times do we want to run the model? Starting off with making it run once
n_people <- 64    #How many people are at a party?
n_tables <- 8     #for round & square
n_seats <- 8      # tables
indslag <- NA     #no added external stimuli yet
boundent_move <- NA #no added restricted move time yet
tics <- 20 #each tic is 30 minutes = 10 hours of parting
df_collected <- tibble(iteration = rep(seq(1,100),3),
       table_type = rep(c(1,2,3),each=100),
       party = rep(vector("list", length = 300)),
                                   pre_network = rep(vector("list", length = 300)),
                                   post_network = rep(vector("list", length = 300))

       )

```

## Set the tables
- Make contact networks
structure is table (1:8), seat (1:8), indices for contact seats (1:8) with 1:5 contact seats, and their seat number depending on which table they are seated at (fx. table 1 seat 1 = new_Seat 11).

They are saved in this workspace
```{r saved tables}
#do this three times for each type of table/party
table_type <- vector("list", length = 3)
table_type[[1]] <- long_table
table_type[[2]] <- round_tables
table_type[[3]] <- square_tables

#column 3 in all dataframes have to be ID
```

```{r round}
#input the seatno with the current seatno can make contact with in the contactseatno
#round
round_tables <- tibble(expand.grid(table = seq(n_tables), seat = seq(n_seats), ID = 0, indices=NA))
#add table no to their seat no
round_tables$new_seat <-paste(round_tables$table, round_tables$seat, sep='') 


# make contact seats
for (i in 1:nrow(round_tables)) {
   seat <- round_tables$seat[i]
   
   # Calculate the indices for the contact seats
   if (seat == 1 ){
     indices <- c(2,8)}
   else if (seat == 2){
     indices <- c(1,3)}
   else if (seat == 3){
     indices <- c(2,4)}
   else if (seat == 4){
     indices <- c(3,5)}
   else if (seat == 5){
     indices <- c(4,6)} 
   else if (seat == 6){
     indices <- c(5,7)}  
   else if (seat == 7){
     indices <- c(6,8)}  
   else if (seat == 8){
     indices <- c(7,1)} 
  #add to index
  index <- c()
  for (n in 1:length(indices)){
    idx <- paste(round_tables$table[i], indices[n],sep='')
    index <- c(index,idx)
  }
  round_tables$indices[i] <- paste(index, collapse = ', ')

}

```

```{r square}
#square
square_tables <- tibble(expand.grid(table = seq(n_tables), seat = seq(n_seats), ID = 0, indices =NA))
square_tables$new_seat <- paste(square_tables$table, square_tables$seat, sep='') 


# make contact seats
for (i in 1:nrow(square_tables)) {
   seat <- square_tables$seat[i]
   
   # Calculate the indices for the contact seats
   if (seat == 1 ){
     indices <- c(2,3,4,7,8)}
   else if (seat == 2){
     indices <- c(1,3,4,7,8)}
   else if (seat == 3){
     indices <- c(1,2,4,5,6)}
   else if (seat == 4){
     indices <- c(1,2,3,5,6)}
   else if (seat == 5){
     indices <- c(3,4,6,7,8)} 
   else if (seat == 6){
     indices <- c(3,4,5,7,8)}  
   else if (seat == 7){
     indices <- c(5,6,8,1,2)}  
   else if (seat == 8){
     indices <- c(5,6,7,1,2)} 
  #add to index
  index <- c()
  for (n in 1:length(indices)){
    idx <- paste(square_tables$table[i], indices[n],sep='')
    index <- c(index,idx)
  }
  square_tables$indices[i] <- paste(index, collapse = ', ')

}

```

```{r long}
n_people <- 64
#long
long_table <- tibble(table=1,seat=1:n_people,ID=0,indices=NA)
# Iterate over each row in the dataframe
for (i in 1:nrow(long_table)) {
   seat <- i
     # Calculate the indices for the contact seats
   #corners
   if (seat == 1 ){
     indices <- c(seat + 1, seat + 2, seat + 3)}
   else if (seat == 2 ){
     indices <- c(seat - 1, seat + 1, seat + 2)}
   else if (seat == n_people -1){
     indices <- c(seat + 1, seat - 2, seat - 1)}
   else if (seat == 64){
     indices <- c(63, 62, 61)}
   #index +3 and -3, for some reason is off...
   else if (seat == 3){
     indices <- c(seat-1,seat-2,seat+1,seat+2,seat+3)
   }
   else if (seat == n_people-2){
     indices <- c(seat-1,seat-2,seat+1,seat+2,seat-3)
   }
   #the rest
   else if (seat %% 2){
     indices <- c(seat - 3, seat - 2, seat - 1, seat + 1, seat + 2)
   } else {
     indices <- c(seat - 1, seat - 2, seat + 1, seat + 2, seat + 3)
   }
  # Remove any indices that are out of bounds
  indices <- indices[indices > 0 & indices < n_people+1]
  #add to index
  n_indices <- length(indices)
  index <- c()
  for (n in 1:n_indices){
    index <- c(index,indices[n])
  }
  long_table$indices[i] <- paste(index, collapse = ', ')

}

```

## Make hosts

```{r make hosts}
### Define hosts of parties ###

# All host shares at least 1 interest with everyone, and are connected to all guests
make_hosts <- function(number_of_iterations){ 
  max_hosts <- iterations+100 #define the highest host id (+100 to make hosts identifiable)
    
  hosts <<- tibble(
      ID = 101:max_hosts, #+100 to give the hosts identifyable ID's
      ie = sample(1:9, iterations, replace = TRUE, prob =  ie_prob),    #introvert / extrovert scale from 1-9, from Emma and Mie
      n_closefriends = n_people, #friends with every one at the party
      #in the tryout markdown the randomization of interest was tested an only a few combination was shown twice, therefore we will not do anything further to randomize the selected interests.
      interest1 = sample(1:14, iterations, replace = TRUE, prob = int_prob),
      interest2 = sample(1:14, iterations, replace = TRUE, prob = int_prob),
      interest3 = sample(1:14, iterations, replace = TRUE, prob = int_prob),
      weight_time = round((runif(iterations, min = -1, max = 1)),digits = 2),#testing to make weights for the satisfaction rate
      weight_interest = 1-abs(weight_time)#testing to make weight for the satisfaction rate
    )
}
``` 
  
## Make party
```{r setup people for party}
### Choosing who the guests are at all parties
make_party <- function(index_of_current_iteration){
  i <- index_of_current_iteration
  
  ###selecting a host####
  host <- hosts[i,]
  host_interest <- c(host$interest1,host$interest2,host$interest3)
  
  ###making guests###
  
  #Assigning variables to guests 
  guests <- tibble(ID = 2:n_people-1, #Creating 63 people
                    ie = sample(1:9, n_people-1, replace = TRUE, prob =  ie_prob), #Introvert/extrovert values to people
  
                    n_closefriends = sample(1:10, n_people-1, replace = TRUE, prob = ven_prob[1:10]), #Amount of close friends (everyone has at least one friend (the host))
                   
                    interest1 = sample(host_interest,n_people-1,replace=TRUE), #choose a random interest that fits with the host
                    interest2 = sample(1:14, n_people-1, replace = TRUE, prob = int_prob),
                    interest3 = sample(1:14, n_people-1, replace = TRUE, prob = int_prob),
                   
                    weight_time = round((runif(n_people-1, min = -1, max = 1)),digits = 2),#testing to make weights for the satisfaction rate
                    weight_interest = 1-abs(weight_time)#testing to make weight for the satisfaction rate
  )
  ### make the party ###
  party <- rbind(host,guests)
  party <<- party %>% 
    mutate(friend_id=NA) %>% 
    mutate(satisfaction_baseline = sample(1:9, n_people, replace = TRUE, prob =  soba_prob)) %>% # not simulated yet, CANNOT BE ZERO
    mutate(satisfaction = 0) %>% 
    mutate(moves = 0) %>%  #how their satisfaction if moved according
    mutate(decision_move = NA)

}
```

## Prenetwork
```{r friends network}
make_prenetwork <- function(party_dataframe){
  party <- party_dataframe

  ### Creating a network of the connections pre-party###
  pre_network <- expand.grid(from=party$ID,to=party$ID)
  pre_network$weight <- 0
  pre_network <- filter(pre_network, from != to)
  
  ### Assigning friends to everyone
  for (i in 1:nrow(party)) {
    num_friends <- party$n_closefriends[i]  # Get the number of friends for the current person
    id_pool <- party$ID[-i]  # Exclude the current person's ID from the pool of potential friends
    
    ids_above_100 <- id_pool[id_pool > 100] #Separate people into host and guests
    ids_below_100 <- id_pool[id_pool <= 100]
    
    # If the current person needs to have more than 1 friend (more than just the host)
    if (num_friends > 0) {
      friend_ids_above_100 <- ids_above_100
      # Add all IDs above 100 as friends
      remaining_friends <- num_friends - 1

      # Randomly select additional friend IDs from below 100
      friend_ids_below_100 <- sample(ids_below_100, size = remaining_friends, replace = FALSE)
      
      # Combine the friend IDs
      friend_ids <- c(friend_ids_above_100, friend_ids_below_100)
    } else {
      # Randomly select friend IDs from above 100
      friend_ids <- sample(ids_above_100, size = num_friends, replace = FALSE)
    }

    # Assign the selected friend IDs to the corresponding row in the dataframe
    party$friend_id[i] <- paste(friend_ids, collapse = ', ')
    party <<- party #save to environment
  }
  
  #Add weight to all the friendships we just created
  for (i in 1:nrow(party)){
    current_id <- party$ID[i]
    temp <- pre_network %>% filter(from==current_id)
     for (k in strsplit(party$friend_id[i], ", ")[[1]]){
       temp2 <- temp %>% filter(to==k)
       temp2$weight <- temp2$weight + 30
       temp <- temp %>% filter(to!=k)
       temp <- rbind(temp2, temp)
    }
      pre_network <- pre_network %>% filter(from!=current_id)
      pre_network <- rbind(pre_network, temp)
  }
  #save to environment
 pre_network <<- pre_network
}
```



# Running ABM
**remember to load probabilities, table types and global variables beforehand**

```{r ABM}



start <- format(Sys.time(),"%HH %MM %SS")


for (p in 1:length(table_type)){

  table <- table_type[[p]]
  
  #make hosts
  hosts <- make_hosts(iterations)
  
  
  #repeat x times for each type of table/party
  for (i in 1:iterations){
    df_index <- which(df_collected$table_type== p & df_collected$iteration==i)
    df_collected$table_type[df_index] <- if (p == 1) "long" else if (p == 2) "round" else "square"
    
    print(paste("starting ", i, " out of ", iterations, " iterations for ", df_collected$table_type[df_index], " table"))
    
    #make party
    party <- make_party(i)
    
    #make prenetwork
    network <- make_prenetwork(party)
    
    #save prenetwork
    df_collected$pre_network[[df_index]] <- network

    
    #seat everybody to start off
    #get people
    no_seat <- party$ID

    #shuffle
    no_seat <- no_seat[sample(length(no_seat))]
    # assign people seats
    table$ID[table$ID==0] <- sample(no_seat, size = length(no_seat), replace = FALSE)
    no_seat <- c()
    
    #start party
    for (tic in 1:tics){
    print(paste("starting ", tic, " out of ", tics, " tics "))

      for (person in party$ID){#do this for each person
        person_table <- which(table$ID==person)
        person_party <- which(party$ID==person)
        
      #look at contact seats
        #get ID's for people sitting in contact seats
        #get contact seats
        con_indices <- as.numeric(strsplit(table$indices[person_table], ",\\s*")[[1]])
        #get the ID for the contact seats
        con_people <- c()
        if (p == 1){
          for (ci in con_indices){
            con_person <- table[ci,3][[1]] #column 3 in all dataframes have to be ID
            # Combine the friend IDs
            con_people <- c(con_people, con_person)
            #save in right format
            con_people <- paste(con_people, collapse = ', ')
            con_people <- as.numeric(strsplit(con_people, ",\\s*")[[1]])
          }
        }else if (p == 2 | p == 3){
          for (ci in con_indices){
          con_person_index <- which(table$new_seat==ci)
          con_person <- table[con_person_index,3][[1]] #column 3 in all dataframes have to be ID
          # Combine the friend IDs
          con_people <- c(con_people, con_person)
          #save in right format
          con_people <- paste(con_people, collapse = ', ')
          con_people <- as.numeric(strsplit(con_people, ",\\s*")[[1]])
          }
        }
        
        #make a dataframe with surrounding peoples variables
        relation_possibilities <- tibble(seat=con_indices,ID=con_people, outcome=0, n_interest = 0, friendshipscore = 0, decision = 0,commitment=0)
        #fill
        for (cp in con_people){
              #in n_interest
          row2 <- which(party$ID == cp)

          # Get the values in the columns for the specified rows
          values_row1 <- party[person_party, c("interest1", "interest2", "interest3")]
          values_row2 <- party[row2, c("interest1", "interest2", "interest3")]
          
          # Check if the values are identical for the two rows
          rp_cp <- which(relation_possibilities$ID== cp)
          relation_possibilities$n_interest[rp_cp] <- sum(sapply(values_row1, function(x) any(values_row2 %in% x)))
          
             #friendshipscore
          row_index <- which(network$from == person & network$to == cp)
          relation_possibilities$friendshipscore[rp_cp] <- network$weight[row_index]
          
            # outcome column
          wf <- party$weight_time[person_party][[1]]
          wa <- party$weight_interest[person_party][[1]]
          relation_possibilities$outcome[rp_cp] <- wf *
            relation_possibilities$friendshipscore[rp_cp] + wa *
            relation_possibilities$n_interest[rp_cp] #watch out since old friend weigh heavily in this equation, hopefully it will surfice
          
        }
        
        #determine commitment
        for (cp in con_people){
          rp_cp <- which(relation_possibilities$ID== cp)
          rp_cp_com <- relation_possibilities %>% 
            filter(ID != cp)
          relation_possibilities$commitment[rp_cp] <- relation_possibilities$outcome[rp_cp] + (iterations - i +1) - max(relation_possibilities$outcome, na.rm =TRUE)
            
        }
        
        #make decision whether to become friends
        # Define a threshold value
        threshold <- 0.5 #arbitrary
        # Convert values to yes(1) or no(0) answer
        relation_possibilities$decision <- ifelse(relation_possibilities$commitment >= threshold, 1, 0)
        #evaluate friendshipstatus
        #add 1 weight from the parson wanting the relationsship
        for (cp in con_people){
        rp_cp <- which(relation_possibilities$ID == cp)
        row_index <- which(network$from == person & network$to == cp)
        network$weight[[row_index]] <- network$weight[[row_index]] + relation_possibilities$decision[[rp_cp]]
        }


      #calculate proximity
        #check whether peoples current friends are near (meaning whether they are within contact seats)
        #get who we are looking at
        prox <- network %>% 
          filter(weight!=0) %>% 
          filter(from == person)
        prox_friends <- c() #empty vector to store friend ID's
        for (ap in 1:nrow(prox)){
          friend <- prox$to[ap]
          prox_friends <- c(prox_friends,friend)
        }

        check_friends_nearby <- sum(sapply(con_people, function(x) any(prox_friends %in% x))) #number of true instances of there contact_people overlap with current friend network
        
      #evalute overall satisfaction
          party[person_party, "satisfaction"][[1]] <- party[person_party, "satisfaction_baseline"][[1]] + check_friends_nearby #guests satisfaction is updated with the percentage of the people that they can sit next to actually are their friends (have a weight above 0) currently


      #decide whether to move
        # Define a threshold value
        threshold <- 1 - party$ie[person_party]/10 #percent needed for people to make a decision e.g. ie = 9 (extrovert) /10 = 0,9 1-0,9 = 0,1 = 10% change needed for them to stay
          #change
          change <- (party$satisfaction[person_party] - party$satisfaction_baseline[person_party]) / party$satisfaction_baseline[person_party]
        # Convert values to yes(1) or no(0) answer
        party[person_party, "decision_move"][[1]] <- ifelse(change > threshold, "no", "yes") #if the change is bigger than your threshold, than you are satisfied and stay seated decions_move ="no"
      #assuming person index = person, no_seat list exists
        
      } #go from individual to global level
      
      for (person in party$ID){#do this for each person
        person_table <- which(table$ID==person)
        person_party <- which(party$ID==person)
        if (party[person_party, "decision_move"][[1]] == 'yes'){
          #add one to move count
          party[person_party, "moves"][[1]] <- party[person_party, "moves"][[1]] + 1
          #remove from their seat
          table[person_table,"ID"][[1]] <- 0
          #add to no seat
          new_no_seat <- c(person)
          no_seat <- c(no_seat,new_no_seat)
        } #else stay seated
      }
      
      #seat everyone
      table$ID[table$ID==0] <- sample(no_seat, size = length(no_seat), replace = FALSE)
      #clear out no_seat_list
      no_seat <- c()

      
    } #after all tics
    
    #save postnetwork
    df_collected$post_network[[df_index]] <- network
    #save party
    df_collected$party[[df_index]] <- party
    

  }
  
}
#save workspace instead
#save.image("ABM.RData")
#write.csv(df_collected, file = "ABM_dataframe.csv")

end <- format(Sys.time(),"%HH %MM %SS")

#duration of running abm
# Convert time values to POSIXlt objects
start_time <- strptime(start, "%HH %MM %SS")
end_time <- strptime(end, "%HH %MM %SS")

# Calculate time difference
time_diff <- end_time - start_time


# Print the time difference
print(paste("It took ", time_diff, "minutes to run ", iterations, " iterations for ", length(table_type), "table types"))


```

# Investigate ABM
```{r test hosts}
#check it out
# head(hosts)
#seems good

#could be fun to make a radar chart of the hosts
#https://www.datanovia.com/en/blog/beautiful-radar-chart-in-r-using-fmsb-and-ggplot-packages/
#opar <- par() 
# Define settings for plotting in a 3x4 grid, with appropriate margins:
#par(mar = rep(0.8,3))
#par(mfrow = c(3,3))
# Produce a radar-chart for each student
#for (i in 1:nrow(hosts)) {
 # radarchart(
  #  hosts[c(2:7, i), ],#hosts[ i,c(2:7)]
   # pfcol = c("#99999980",NA),
    #pcol= c(NA,2), plty = 1, plwd = 2,
#    title = row.names(hosts)[i]
 # )
#}
# Restore the standard par() settings
#par <- par(opar) 
```

```{r test interest overlap}
# par(mfrow=c(1,3))
# plot(density(hosts$interest1))
# plot(density(hosts$interest2))
# plot(density(hosts$interest3))
# #library(plyr)
# dplyr::count_(hosts, vars = c('interest1','interest2','interest3'))
# aggregate(ID ~ ., hosts, FUN = length)
# 
# dupes <- apply(hosts[,2:4], 1, function(x) any(duplicated(x)))
# dupes <- hosts[dupes, ]
# dup <- dupes[1,]
# stringr::str_count(dupes) #18 true #four characters, =28 procent had an overlap in at least two coloumns
```

```{r test interest overlap}
# #test if people have overlap in interests within themselves
# dupes <- apply(guests[,5:7], 1, function(x) any(duplicated(x)))
# stringr::str_count(dupes) #16 true #four characters, =25 procent had an overlap in at least two coloumns

```

```{r plot packages}
#Plotting Friendship network
pacman::p_load(tidyverse,
               here,
               network,
               igraph,
               ggraph,
               tidygraph,
               patchwork,
               bootnet)

```

```{r plot prenetwork}
pacman::p_load(tidyverse,
               here,
               network,
               igraph,
               ggraph,
               tidygraph,
               patchwork)
nodes <- party$ID

pre_igraph <-
  graph_from_data_frame(d = df_collected$pre_network[[1]],
                        vertices = nodes,
                        directed = TRUE)


pre_igraph <- simplify(pre_igraph, 
                                  remove.multiple = TRUE, 
                                  remove.loops = TRUE,
                                  edge.attr.comb = igraph_opt("edge.attr.comb"))



E(pre_igraph)$arrow.mode <- 0



V(pre_igraph)$label <- "" 

V(pre_igraph)$frame.color <- "white"
V(pre_igraph)$color <- "orange"
E(pre_igraph)$width <- edge_attr(pre_igraph)$weight/16 #this one adjusts the size of arrows 
#E(pre_igraph)$arrow.size <- 0.01
plot(pre_igraph,
     layout=layout_nicely,
     #vertex.label= V(pr,
     edge.arrow.size=0.01#,
     #vertex.label.color = "black",
     #vertex.size=node.size
     )

#ask Emma how to make their cool network plot
```

```{r plot network at round tables}
round <- expand.grid(from=round_tables$new_seat,to=round_tables$new_seat)
round$weight <- 0
round <- filter(round, from != to)
#Add weight to all the friendships we just created
for (i in 1:nrow(round_tables)){
  current_id <- round_tables$new_seat[i]
  temp <- round %>% filter(from==current_id)
   for (k in strsplit(round_tables$indices[i], ", ")[[1]]){
     temp2 <- temp %>% filter(to==k)
      temp2$weight <- temp2$weight + 1
       temp <- temp %>% filter(to!=k)
      temp <- rbind(temp2, temp)
  }
    round <- round %>% filter(from!=current_id)
    round <- rbind(round, temp)
}

# for visualisation
round <- round[!(round$weight==0),]
round_graph <-
  graph_from_data_frame(d = round,
                        vertices = round_tables$new_seat,
                        directed = TRUE)
V(round_graph)$label <- "" 

plot(round_graph,
     layout = layout_nicely, # Explore layouts!
     edge.arrow.size = 0.2) 
```

```{r plot network at square tables}
square <- expand.grid(from=square_tables$new_seat,to=square_tables$new_seat)
square$weight <- 0
square <- filter(square, from != to)
#Add weight to all the friendships we just created
for (i in 1:nrow(square_tables)){
  current_id <- square_tables$new_seat[i]
  temp <- square %>% filter(from==current_id)
   for (k in strsplit(square_tables$indices[i], ", ")[[1]]){
     temp2 <- temp %>% filter(to==k)
      temp2$weight <- temp2$weight + 1
       temp <- temp %>% filter(to!=k)
      temp <- rbind(temp2, temp)
  }
    square <- square %>% filter(from!=current_id)
    square <- rbind(square, temp)
}

# for visualisation
square <- square[!(square$weight==0),]
square_graph <-
  graph_from_data_frame(d = square,
                        vertices = square_tables$new_seat,
                        directed = TRUE)
V(square_graph)$label <- "" 
E(square_graph)$width <- edge_attr(square_graph)$weight

plot(square_graph,
     layout = layout_on_grid, # Explore layouts!
     edge.arrow.size = 0.2) 
```

```{r plot network at long table}
long <- expand.grid(from=long_table$seat,to=long_table$seat)
long$weight <- 0
long <- filter(long, from != to)
#Add weight to all the friendships we just created
for (i in 1:nrow(long_table)){
  current_id <- long_table$seat[i]
  temp <- long %>% filter(from==current_id)
   for (k in strsplit(long_table$indices[i], ", ")[[1]]){
     temp2 <- temp %>% filter(to==k)
      temp2$weight <- temp2$weight + 1
       temp <- temp %>% filter(to!=k)
      temp <- rbind(temp2, temp)
  }
    long <- long %>% filter(from!=current_id)
    long <- rbind(long, temp)
}

# for visualisation
long <- long[!(long$weight==0),]
long_graph <-
  graph_from_data_frame(d = long,
                        vertices = long_table$seat,
                        directed = TRUE)
V(long_graph)$label <- "" 


plot(long_graph,
     layout = layout_in_circle, # Explore layouts!
     edge.arrow.size = 0.2) 

```

```{r plot post_network}
pacman::p_load(tidyverse,
               here,
               network,
               igraph,
               ggraph,
               tidygraph,
               patchwork)
nodes <- party$ID

post_igraph <-
  graph_from_data_frame(d =df_collected$post_network[[1]],
                        vertices = nodes,
                        directed = TRUE)


post_igraph <- simplify(post_igraph, 
                                  remove.multiple = TRUE, 
                                  remove.loops = TRUE,
                                  edge.attr.comb = igraph_opt("edge.attr.comb"))



E(post_igraph)$arrow.mode <- 0



V(post_igraph)$label <- "" 

V(post_igraph)$frame.color <- "white"
V(post_igraph)$color <- "orange"
E(post_igraph)$width <- edge_attr(post_igraph)$weight/16 #this one adjusts the size of arrows 
#E(post_igraph)$arrow.size <- 0.01
plot(post_igraph,
     layout=layout_nicely,
     #vertex.label= V(pr,
     edge.arrow.size=0.01#,
     #vertex.label.color = "black",
     #vertex.size=node.size
     )

#ask Emma how to make their cool network plot
```